### 2020-01-31 Paper_EV/Paper_EV.tex
Update backup data

- Some facts about Crazyflie hardware (foto, uC frequency, weight, length)

@@

- Estimation of relevant components (Matrices...)\\
- Testing of the PD-gains\\
- Testing the filter

\subsection{Structure} \label{subsec:Structure}
- Force frame from B to O for an easy representation\\
- Show each equation of forces with explaining the made assumptions\\
- Parameters\\
- Actuator dynamics\\
- Filter\\
- Images of the Simulink model

@@

@@

- Actuator Dynamics (Estimation of the time constant) \\
- Estimation of the control effectiveness parameters G1, G2

@@

\subsection{Testing with contact Forces and Moments} \label{subsec:testing_with_fandm}

@@

>>>>

- Some facts about Crazyflie hardware (foto, uC frequency, weight, length (foto of lever arms), onboard sensors, additional sensors/HW (optoflow, sd-card))

@@

- Estimation of the relevant for the HW implementation components (which terms make a huge impact on the controller performance: G1, G1 etc)\\
- Estimate where value explosion can occur\\
- Testing the behaviour of the filter\\
- Testing of the PD-gains

\subsection{Structure} \label{subsec:Structure}
- Describe some assumptions: eg newton second law frame transformation from B to O for an easy representation\\
- Present each equation of forces with explaining made assumptions\\
- Parameter choice ($k_F$, $k_M$, ...)\\
- Describe the actuator dynamics modelling\\
- Describe the filter transfer function\\
- Images of the Simulink model

@@

- Plot differences with or without some terms (G1, G2\_yaw) \\

@@

- Actuator Dynamics (Estimation of the time constant), plot response with estimated constant\\
- Estimation of the control effectiveness parameters G1, G2 for inner INDI (describe performed flight to log data), plot the curve with contribution of G1, G2 to the fitting\\
- PD gain tuning for inner INDI (using pd\_inner\_cs(), show plots with different D-gains (e.g 25, 10 and 3) to see different damping behaviour), Before explaining gain tuning present all relevant transfer functions of the closed and open loops\\
- Outer loop (show new diagram of the controller)

@@

\subsection{Testing with contact Forces and Moments?} \label{subsec:testing_with_fandm}

@@

- To make the controller work a minimal knowledge of the system dynymics is need. Nevertherless G1, G2 still have to estimated accuratly because this 2 parameters do have inpact on the controller performance.
